Improving credibility and efficiency of decision-making \\ within democratic communities via a statistical quorum

### 2018-04-19 statistical-quorum.tex
Changes to voting.
submission v1

Past approaches exist in using Bayesian statistics in the context of voting theory.  In particular, Bayesian methods have been proposed for auditing election outcomes \citep{rivest2012bayesian}.  Many further methods have been developed for efficient ballot auditing \cite{lindeman2012bravo}, \citep{rivest2017clipaudit}.  The problem of verifying an election's outcome is mathematically similar in structure to the notion of a statistical quorum defined in this work; however, a critical difference lies in the role the metric plays in the decision-making process itself.  Post hoc verification of results does not influence voting.  A statistical quorum, on the other hand, directly influences the allocation of a community's attention by essentially performing voting audits in real-time. To our knowledge, no methods have been formalized for coupling the verification of vote outcomes with the voting process itself. Furthermore, the dynamic statistical quorum presented here takes the previous ideas one step further.  Statistical method for auditing vote outcomes have no way to infer what we call the ``effective population size'', i.e., the portion of the population that actually cares about a vote's outcome.  We believe this information is crucial and have developed new statistical methods to infer this population and subsequently couple it to the statistical quorum, further influencing the influence on the decision-making process itself.  Additional work exists for selectively sampling a subset of the voting population to estimate the population's bias \cite{chaum2016random}. In random-sample voting, the emphasis is on security and efficiency of voting.  The approach taken to optimally allocate a community's attention is fundamentally different, however, in that the goal is to selectively distribute votes to random subsets of the population with the intent of reducing the amount of attention required by each individual.  This does indeed reduce the amount of attention required of individual voters, but at the same time is restricts the freedom of voters to participate only in the votes they have been delegated to participate in.

@@

In the case of the in-person decision making it is also unclear how much time to spend on each
discussion item: how contentious the discussion really is can be seen only after voting.
Using PeerMind members can observe the voting process in real-time and continue discussing
and even changing their votes if they get convinced to change their position.
At the same time using feedback provided by credibility value they can also gauge how
much discussion is needed.

% People changed vote online X times after discussion.

@@

>>>>

Past approaches exist in using Bayesian statistics in the context of voting theory.  In particular, Bayesian methods have been proposed for auditing election outcomes \citep{rivest2012bayesian}.  Many further methods have been developed for efficient ballot auditing \cite{lindeman2012bravo}, \citep{rivest2017clipaudit}.  The problem of verifying an election's outcome is mathematically similar in structure to the notion of a statistical quorum defined in this work; however, a critical difference lies in the role the metric plays in the decision-making process itself.  Post hoc verification of results does not influence voting.  A statistical quorum, on the other hand, directly influences the allocation of a community's attention by essentially performing voting audits in real-time. To our knowledge, no methods have been formalized for coupling the verification of vote outcomes with the voting process itself.

Furthermore, the dynamic statistical quorum presented here takes the previous ideas one step further.  Statistical method for auditing vote outcomes have no way to infer what we call the ``effective population size'', i.e., the portion of the population that actually cares about a vote's outcome.  We believe this information is crucial and have developed new statistical methods to infer this population and subsequently couple it to the statistical quorum, further influencing the influence on the decision-making process itself.

Additional work exists for selectively sampling a subset of the voting population to estimate the population's bias \cite{chaum2016random}. In random-sample voting, the emphasis is on security and efficiency of voting.  The approach taken to optimally allocate a community's attention is fundamentally different, however, in that the goal is to selectively distribute votes to random subsets of the population with the intent of reducing the amount of attention required by each individual.  This does indeed reduce the amount of attention required of individual voters, but at the same time is restricts the freedom of voters to participate only in the votes they have been delegated to participate in.

@@

In the case of the in-person decision making it is also unclear how much time to spend on each
discussion item: how contentious the discussion really is can be seen only after voting.
Using PeerMind members can observe the voting process in real-time and continue discussing
and even changing their votes if they get convinced to change their position.
69 members changed a total of 279 votes 60 minutes or later after their first vote when
using PeerMind.
At the same time using feedback provided by credibility value they can also gauge how
much discussion is needed.

@@

In this work we have developed a theoretical framework of computing statistical credibility
of decisions being made through a voting process.
We applied this framework to design a statistical quorum which we integrated with a web application
PeerMind.
We deployed the application in a democratic community to compare its effect in comparison with
prior time before the introduction of the web application.
Analyzing the effects of this introduction, we conclude that our hypothesis that using
credibility as a feedback mechanism and statistical quorum as a threshold really improves
the participation of members in decision making, making it more inclusive, more engaging, and
better spend collective attention available for decision making.
